Virtualization of a Real-Time Operating System for Robot Control with a Focus on Real-Time Compliance

### 2024-09-02 Masterarbeit_Robotik_Pamuk.tex
Fertiggggg

\begin{table}[H]
	\centering
	\footnotesize
	\caption{Comparison of Latency Statistics in Salamander 4 after Configurations}
	\label{tab:latency_tables_combined}
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{Salamander 4 Version}      & \textbf{Lat Min (µs)} & \textbf{Lat Avg (µs)} & \textbf{Lat Max (µs)} & \textbf{Overruns} \\ \hline
		Salamander 4 Bare Metal      & 0.613                 & 1.380                 & 10.709                & 0                 \\ \hline
		Untuned Salamander 4 Virtualization & 2.536                 & 8.940                 & 707.622               & 43                \\ \hline
		After BIOS Configurations     & 0.969                 & 3.948                 & 457.545               & 22                \\ \hline
		After Kernel Configurations   & 2.545                 & 4.811                 & 21.694                & 0                 \\ \hline
		After Host Configurations     & 2.591                 & 4.834                 & 18.441                & 0                 \\ \hline
		After QEMU Configurations     & 2.614                 & 4.779                 & 17.134                & 0                 \\ \hline
	\end{tabular}
\end{table}

@@

\begin{table}[H]
	\small
	\centering
	\caption{Comparison of Robotic Application Latency Statistics}
	\label{tab:robotic_application_latency_values_combined}
	\setlength{\tabcolsep}{0.5em} % for the horizontal padding
	{\renewcommand{\arraystretch}{1.2}% for the vertical padding
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			\textbf{Version}        & \textbf{Lat Min (ms)} & \textbf{Lat Avg (ms)} & \textbf{Lat Max (ms)} & \textbf{Std Dev (ms)} \\ \hline
			Salamander 4 Bare Metal              & 1.211                 & 1.347                 & 1.49                  & 0.082                 \\ \hline
			Untuned Salamander 4 Virtualization & 3.1                   & 24.603                & 129.46                & 13.876                \\ \hline
			Tuned Salamander 4 Virtualization   & 1.219                 & 2.62                  & 3.988                 & 0.812                 \\ \hline
		\end{tabular}}
\end{table}

>>>>

\begin{table}[H]
	\centering
	\small
	\caption{Comparison of Latency Statistics in Salamander 4 after Configurations}
	\label{tab:latency_tables_combined}
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{Salamander 4 Version}      & \textbf{Lat Min (µs)} & \textbf{Lat Avg (µs)} & \textbf{Lat Max (µs)} & \textbf{Overruns} \\ \hline
		Salamander 4 Bare Metal      & 0.613                 & 1.380                 & 10.709                & 0                 \\ \hline
		Untuned Salamander 4 Virtualization & 2.536                 & 8.940                 & 707.622               & 43                \\ \hline
		After BIOS Configurations     & 0.969                 & 3.948                 & 457.545               & 22                \\ \hline
		After Kernel Configurations   & 2.545                 & 4.811                 & 21.694                & 0                 \\ \hline
		After Host Configurations     & 2.591                 & 4.834                 & 18.441                & 0                 \\ \hline
		After QEMU Configurations     & 2.614                 & 4.779                 & 17.134                & 0                 \\ \hline
	\end{tabular}
\end{table}

@@

\begin{table}[H]
	\small
	\centering
	\caption{Comparison of Robotic Application Latency Statistics}
	\label{tab:robotic_application_latency_values_combined}
	\setlength{\tabcolsep}{0.5em} % for the horizontal padding
	{\renewcommand{\arraystretch}{1.2}% for the vertical padding
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			\textbf{Salamander 4 Version}        & \textbf{Lat Min (ms)} & \textbf{Lat Avg (ms)} & \textbf{Lat Max (ms)} & \textbf{Std Dev (ms)} \\ \hline
			Salamander 4 Bare Metal              & 1.211                 & 1.347                 & 1.49                  & 0.082                 \\ \hline
			Untuned Salamander 4 Virtualization & 3.1                   & 24.603                & 129.46                & 13.876                \\ \hline
			Tuned Salamander 4 Virtualization   & 1.219                 & 2.62                  & 3.988                 & 0.812                 \\ \hline
		\end{tabular}}
\end{table}
